BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-17 tex/1-intro.tex
Added related work on large scale distributed crawlers$

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, political or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}. The need to preserve this volatile communication medium is nowadays very clear.

@@

A key characteristic of blogs which differentiates them from regular websites is their association with web feeds. Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs. Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata. Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order harvest previous content.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions and Overview}
We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing blogs, extracting their content and monitoring their updates. Our contributions are in particular:\TODO{NK: Instead: "In this paper:"}

>>>>

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, political or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}. The need to preserve this volatile communication medium is nowadays very clear.

@@

A key characteristic of blogs which differentiates them from regular websites is their association with web feeds. Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs. Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata. Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest previous content.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions and Overview}
We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing blogs, extracting their content and monitoring their updates. Our contributions are in particular:

### 2014-01-17 tex/2-related-work.tex
Added related work on large scale distributed crawlers$

- Web crawlers

we merged the crawling phase with the contente extraction which removed the need to store all web pages material and leads to a lighter process as we directly send things to the db

- Blog crawlers
focused on blog detection and content analysis such as political mouvement or popular personalities.

- Wrapper generation
these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.

>>>>

\Anotecontent{wrapper}{In the literature, procedures to extract structured data from unstructured document are commonly referred as \emph{wrappers}. In this paper we decided to rather employ the less generic term of \emph{extraction rules} which is closer to our implementation.}

The BlogForever Crawler combines ideas from previous work on general web crawlers and extraction rule\Anote{wrapper} generation algorithms.

Research on large scale distributed crawler such as Mercator \cite{najork2001}, used by AltaVista, the spider discussed in \cite{shkapenyuk2002} or UbiCrawler \cite{boldi2003} are enlightening regarding the difficulties arising when scale out a crawler. One of the core issues seems to be in sharing the list URLs which have already been visited and need to be visited. While \cite{najork2001} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing. Both of these approaches require complex mechanisms to achieve fault tolerance. The BlogForever crawler circumvent this problem by delegating all state the back-end system. This shared nothing architecture between crawler instance is made possible by the fact that our unit of computations, crawling a entire blog, is much large than fetching a single URL and does not generate further crawling tasks. In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side. This removes one layer of complexity when compared to general crawler which need use a distributed file system or implement an aggregation mechanism in order to further use the collected data.

\cite{shkapenyuk2002} used NFS, \cite{berger2011} uses HDFS

- Wrapper generation\\
these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.
